Factoring with $n+2$ clean qubits and $n-1$ dirty qubits

### 2017-05-08 doc/paper.tex
Better modular double

The conditional offset operations need one dirty bit, and the modular doublings need two, but for non-trivial $n$ there are more than enough unused bits available to borrow, so the circuit as a whole doesn't require any dirty bits.

@@

To multiply a register by 2 modulo an odd $R$, we use pivot-flips (see section \ref{sec:pivot-flips}) and subtraction to align the two halves of the input space to MSB boundaries.
After the two halves are aligned, a left-rotate completes the operation.
See figure \ref{fig:modular-double}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-modular-double.png}
  \caption{\em
    Controlled modular doubling in $O(c + n \lg n)$ gates, $O(c + n)$ depth, with 2 dirty ancilla.
    $R$ must be odd.
    Uses 2 dirty ancilla, $O(c + n \lg n)$ gates, and $O(c + n)$ depth where $c$ is the number of controls and $n$ is the register size.
  }
  \label{fig:modular-double}
\end{figure}

>>>>

The conditional offset and modular doubling operations need one dirty bit, but for non-trivial $n$ there are more than enough unused bits available to borrow, so the circuit as a whole doesn't require any dirty bits.

@@

To multiply a register by 2 modulo an odd $R$, we use controlled offsets and nots to shift the top half of the input space until it starts on the MSB boundary.
Once that's done, a left-rotate completes the operation by turning the MSB into the LSB (converting the alignment into interleaving).
See figure \ref{fig:modular-double}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-modular-double.png}
  \caption{\em
    Controlled modular doubling in $O(c + n \lg n)$ gates, $O(c + n)$ depth, with 2 dirty ancilla.
    $R$ must be odd.
    Uses 1 dirty ancilla, $O(c + n \lg n)$ gates, and $O(c + n)$ depth where $c$ is the number of controls and $n$ is the register size.
  }
  \label{fig:modular-double}
\end{figure}
